Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2015-01-19 misc/SI_thesis.tex
all chapter fine tuned
mini working exmp updated

@@

\chapter{experimental}

@@

@@

For example, the atomic weight of Pb is 207 g/mol, and density is 11.34 g/cm3; then the molar volume is 207/11.34 = 18.2539. Assuming sphere as building unit, then $\frac{\pi}{6}D^3$ = 18.2539/N_A. Solving D as 0.3868 nm.

@@

% Melting points 
\begin{table}[htb]
\centering
\renewcommand*{\thetable}{S\arabic{table}}
\caption{physical constants of reactants }\label{tb:thermo}
\begin{tabular}{lccr}
\toprule
Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & reference\\
\midrule
\ce{NaOH}        & 318 & 1388 & handbook  \\
\ce{NaI}        & 651 & 1300 & MSDS    \\
\ce{KI}        & 681 & 1330 & MSDS   \\
\ce{Na2CO3}        & 851 & Not determined & MSDS    \\
\ce{Na2MoO4}        & 687 & Not available & handbook   \\
\ce{MoO3}    & 795 & 1155 & MSDS   \\
\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
\bottomrule
\end{tabular}
\end{table}

@@

Tungsten bronze: \ce{AxWO3}, or \ce{AxW_{1-x}^{6+}W_x^{5+}O3}, 
Tungstates: \ce{(A2O)x.(WO3)n}, full oxidized, no free electron, transparent in visible and NIR.

>>>>

Functional oxides lie in the doping characteristics: cations with mixed valence states, and anions with vacancies. Vapor-phase growth, powder source is vaporized at an elevated T and .\cite{Dai2003} Dislocation growth mechanism, VS driven by dislocation, kinetics during growth controlled by T and supersaturation ratio. Probability of nucleation and desorption; cation-anion molecules float, the rough structure of the tip; self-catalyzed, where a thin metal layer is present, \cite{Sears1955,Blakely1962}

Thermal evaporation process sensitive to the concentration of oxygen in growth system, influencing not only the volatility of source materials but also the stoichiometry of vapor phase.\cite{Dai2002}

@@

\chapter{experimental}
In this work, magnetron sputtering (Denton Vacuum Desk IV) was used to coat thin layers of metals onto cleaned substrates. As shown in Fig.~\ref{fig:ch2magsp}, a high potential created between the target (cathode) and substrate ionizes the argon molecules. These ions are accelerated to bombard the target foils, knocking out active atoms which subsequently deposit onto the substrates. A magnetic field is applied to confine electrons to the vicinity of the foils. These electrons in turn increase the ionization yield.
Sputtering is a better PVD technique than \gls{ebeam} deposition since it alleviates the adverse effects in the latter. 
Other \gls{ebeam} generated signals, such as Auger electrons, are usually not useful in SEM unless with ultra-high vacuum and clean surface.

@@

\iffalse
The author believe the resolution to a large extent depends on the phase transitions, as discussed in Section.~\ref{sec:wonawo}.

A thin film example on the valency number, color center density. some calculation on doping, uv-vis results on the thin film.

@@

For example, the atomic weight of Pb is 207 g/mol, and density is 11.34 g/cm3; then the molar volume is 207/11.34 = 18.2539. Assuming sphere as building unit, then $\frac{\pi}{6}D^3 = 18.2539/N_A$. Solving D as 0.3868 nm.

@@

% Melting points 
\begin{table}[htb]
\centering
\renewcommand*{\thetable}{S\arabic{table}}
\caption{physical constants of reactants }\label{tb:thermo}
\begin{tabular}{lccr}
\toprule
Material & MP(\si{\degreeCelsius}) & BP(\si{\degreeCelsius}) & Reference\\
\midrule
\ce{NaOH}        & 318 & 1388 & \cite{crc1977}  \\
\ce{NaI}        & 651 & 1300 & \cite{crc1977}    \\
\ce{KI}        & 681 & 1330 & \cite{crc1977}   \\
\ce{Na2CO3}        & 851 & Not determined & \cite{crc1977}    \\
\ce{Na2MoO4}        & 687 & Not available & \cite{crc1977}   \\
\ce{MoO3}    & 795 & 1155 & \cite{crc1977}   \\
\ce{MoO2}    & 1100(decomp) & Not available & MSDS   \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[htb]
\centering
\caption{Comparison of Raman shift (\si{cm^{-1}}) of sodium molybdates and molybdenum oxide}\label{tb:moo3ram}
\begin{tabular}{lllllllll}
\toprule
        & \ce{Na2Mo2O7}    &    &    & \ce{Na2Mo2O7}    &       &       & \ce{MoO3}   &    \\
\midrule
\cite{Saraiva2011} & \cite{Fomichev1992} & this work& \cite{Fomichev1992} & \cite{Schofield2005} & this work   & \cite{Eda1992} & \cite{Siciliano2009}   &  this work   \\
\midrule
 939    & 939/935 & 937         &        & 995    & 995         & 995    & 996       & 996   \\
 921    & 920/918 & 919         & 970    & 971    & 970         & 819    & 819       & 820   \\
 873    & 875/869 & 873         & 960    & 963    & 962         & 666    & 666       & 667   \\
 833    & 836/828 & 833         & 940    &        &             & 471    & 473       &       \\
 821    & 818/815 &             & 925    &        & 926         & 378    & 378       & 380   \\
 768    & 774/765 &             & 910    & 918    & 915         & 366    & 365       & 364   \\
 741    & 741/739 &             & 895    & 899    & 898         & 338    & 337       & 338   \\
 524    & 526/525 &             & 870    &        &             & 291    & 291       & 291   \\
 467    & 464/460 &             & 835    & 841    & 841         & 283    & 283       & 284   \\
 413    & 411/411 &             &        & 820    & 819         & 246    & 244       & 245   \\
 369    & 369/368 & 366         & 745    &        &             & 217    & 218       & 216   \\
 339    & 340/336 & 340         & 650    & 666    &             & 197    & 197       & 199   \\
 295    & 296/294 &             &        & 620    & 619         & 159    & 158       & 156   \\
 249    & 245/245 &             & 438    &        &             & 129    & 129       &       \\
 226    & 228/227 & 226         &        &        & 417         & 117    & 117       &       \\
        & 215/215 &             & 405    &        &             & 100    & 98        &       \\
 200    & 199/199 & 198         &        & 396    & 393         & 84     & 84        &       \\
 176    &         &             & 382    & 381    &             &        &           &       \\
 137    & 140/138 &             &        & 368    &             &        &           &       \\
 120    & 120/120 &             & 348    &        &             &        &           &       \\
 84     & 84/84   &             & 335    & 339    & 336         &        &           &       \\
        & 45/44   &             & 320    & 320    & 318         &        &           &       \\
 36     &         &             & 295    & 293    &             &        &           &       \\
        &         &             & 272    &        & 267         &        &           &       \\
        &         &             & 255    &        &             &        &           &       \\
        &         &             &        & 246    &             &        &           &       \\
        &         &             & 220    & 225    & 224         &        &           &       \\
        &         &             &        & 202    &             &        &           &       \\
        &         &             &        & 159    & 155         &        &           &       \\
        &         &             &        & 131    &             &        &           &       \\
        &         &             &        & 119    &             &        &           &       \\
\bottomrule
\end{tabular}
\end{table}

@@

Tungsten bronze: \ce{A_xWO3}, or \ce{A_xW_{1-x}^{6+}W_x^{5+}O3}, 
Tungstates: \ce{(A2O)x.(WO3)n}, full oxidized, no free electron, transparent in visible and NIR.

### 2015-01-19 misc/draft.tex
After first review in 2014
mini working exmp updated

\chapter{paper draft}
\section{Data Processing}

@@

>>>>

\chapter{paper draft}

\footnote{U.S. Department of Energy, "Energy Efficiency Trends in Residential and Commercial Buildings", 2008.}

\section{Data Processing}

@@

The oxidization of Mo starts at 500 \si{\degreeCelsius}, and \ce{MoO3} vapor pressure begins to increase rapidly above 700 \si{\degreeCelsius}.\cite{Margrave1967} The melting point of \ce{MoO3} is reported as 795 \si{\degreeCelsius}.\cite{Levin1959} Based on these data, the growth was designed with parameters listed in Table~\ref{tab:mooxsi}. It is worth mentioning that these parameters are selected and optimized from a wide range of combinations. When the influence of one parameter is studied, the others are fixed, following the standard practice in controlled experiments.
%growth parameter
\begin{table}[htb]
\centering
\caption{Growth conditions of \ce{MoO3} on Si}\label{tab:mooxsi}
\begin{tabular}{lcccr}
\toprule
&&&\multicolumn{2}{c}{Flow (sccm)} \\
\cmidrule(l){4-5}
 & Temperature $T_h$ (\si{\degreeCelsius}) & Pressure (mTorr) & Ar & \ce{O2}  \\
\midrule
Typical values  & 800    & 200 & 10 & 10  \\
\bottomrule
\end{tabular}
\end{table}

The growth layout is schematically shown in Fig.~\ref{fig:mooxgrowth}. Notice that on the horizontal axis of temperature, zero inch is defined at the upstream edge of furnace. To facilitate discussion and provide a tight context, the author define the position of substrate as the coordinate of its upper-stream edge along this temperature axis, i.e., the substrate location is 7 inch in Fig.~\ref{fig:mooxgrowth}. The usual length of Si substrate is 1 inch. When positioned at 7 inch, it is then located in a temperature zone of $650 \sim 350$ \si{\degreeCelsius}.

From previous works in our group,\cite{predeep2011} it was found that with $T_h = 600$ \si{\degreeCelsius} and substrate placed at 6.5 in, microflakes grew at the high temperature edge of Si, suggesting the nucleation already started.\footnote{in 020510 batch} When flow of oxygen was gradually reduced, diminished size of micro-flake was observed at the same location of substrates. This results indicated the rate-determining step is diffusion when oxygen flow was in the range of 2 sccm to 0.5 sccm. It was also found the deposition amount on a particular location of the substrate is not linearly proportional to the growth time, \emph{i.e.}, the growth at upper stream edge first increase then decrease. This is not surprising when considering the 3D temperature field in chamber requires some time to become synchronized as depicted in Fig.~\ref{fig:mooxgrowth}. Using conditions in Table~\ref{tab:mooxsi} and 2 h growth,

\footnote{http://forum.wordreference.com/showthread.php?t=244497}
